\documentclass{article}
\usepackage{graphicx}

\begin{document}

\title{Questions and Notes}
\author{Victor \& Mikkel}

\maketitle

\section{Questions}
\begin{itemize}
	\item train\_data\_checkpoint.json:\\
	Trained on wikipedia and articles for what purpose?
	To understand "security", "privacy", etc.?
	When is this used?
	\item Commercial intentions?:\\
	Is the intention to use this commercially? 
	The API specifically states that this should not be used commercially. 
	If commercial aspects are of interest, we need to have it approved.
	

\end{itemize}

\section{Notes}
\begin{itemize}
	\item Reddit API:\\
	client ID: fQuRCESlv\_7yOQ\\
	client secret: v6AjzytAKDgqjqyQNczapezXUjk
\end{itemize}

\section{Overview}
\begin{itemize}
	\item reddit\_API.py:\\
	Uses the Reddit API to gather top tweets
	from the "smarthome" subreddit and comments.
	Now set up to use Victor's account.\\
	\emph{Questions}: \\ Why does it not save them?
	How many tweets can/should we get?
	\item scrape.py:\\
	Generates a user-agent to access the different 
	articles used for generating the \textit{train\_data.json} file.\\
	\emph{Questions}: \\ 
	Why are there so many functions for scraping? 
	Is it because they differ in format and need different preprocessing to read?
	\item pushshift\_aggs.py:\\
	Used to scrape the frequency of query-terms 
	\textit{"privacy", "security", "trust"} for the last 3 years on the subreddits. 
	It seems like the \textit{frequency} keyword establishes the sampling rate.
	This is used to plot how many comments uses these query words over 3 years.
	\emph{Questions}: \\ 
	Is this actually the frequency?
\end{itemize}

\end{document}
